\papertitle

### 2012-10-13 manuscript.tex
Various small edits.

We tested our cooperative visual servoing system with a simple target seeking
experiment: the H$^2$Bird must fly through a specified obstacle, in this case,
a wooden frame meant to simulate a window. As the H$^2$Bird cannot detect the
target on its own, we used the ground station to provide remote headings for
navigation to the window. Ground truth data was collected via a motion capture
system in the test room. A sketch of the experimental setup is shown in
Fig.~\ref{fig:experiment_cartoon}.

@@

We simulated the motion of the ornithopter beginning from certain positional
and angular initial conditions using several components representing the
experimental layout of our system described in Fig.~\ref{fig:block_diagram}.
For the "ornithopter dynamics" block, we used the translational model
described by~\ref{eq:total_model_plain} with the angular position model
described by~\ref{eq:transfer_func}. We tuned the PID controller for the
simulation so that paths from known positions looked similar to the behavior
we observed in the experimental data. We also inlcuded the camera capture and
pose estimation delays, and the PID controller sampling rate in the
simulation.

@@

The results of our experimental trials verify the results of the Monte Carlo
simulation of the model that we used. The trials that we conducted in
Fig.~\ref{fig:flight_paths_feasible} correspond to the circled region in
Fig.~\ref{fig:heat_map}. The 80\% success rate that we experienced in the
experiments corroborates our calculated probability of success of
approximately 80\%. Additionally, the diminished success rate of 50\% near the
edges of the viewing triangle that we determined through experimentation
supports the reduced probability of success calculated by the simulation.

>>>>

We tested our cooperative visual servoing system with a simple target seeking
experiment: the H$^2$Bird must fly through a specified obstacle, in this case,
a wooden frame meant to simulate a window. As the H$^2$Bird cannot detect the
target on its own, we used the ground station to provide remote headings for
navigation to the window. A motion capture system in the test room provided
ground truth data. A sketch of the experimental setup is shown in
Fig.~\ref{fig:experiment_cartoon}.

@@

We simulated the motion of the ornithopter beginning from certain positional
and angular initial conditions using several components representing the
experimental layout of our system described in Fig.~\ref{fig:block_diagram}.
For the "ornithopter dynamics" block, we used the translational model
described by~\ref{eq:total_model_plain} with the angular position model
described by~\ref{eq:transfer_func}. We tuned the PID controller for the
simulation so that paths from known positions looked similar to the behavior
we observed in the experimental data. We also account for the camera capture and
pose estimation delays, and the PID controller sampling rate in the
simulation.

@@

The results of our experimental trials verify the results of the Monte Carlo
simulation of our model. The trials that we conducted in
Fig.~\ref{fig:flight_paths_feasible} correspond to the circled region in
Fig.~\ref{fig:heat_map}. The 80\% success rate that we measured in the
experiments corroborates our calculated probability of success of
approximately 80\%. Additionally, the diminished success rate of 50\% near the
edges of the viewing triangle that we determined through experimentation
supports the reduced probability of success calculated by the simulation.
